### 2016-07-01 Projects/DelCo_2012/Report/DelCo_2012.tex
MCFRS added to acknowledgements

Thank you to Chief Scott Goldstein and former Chief Steven Lohr of the Montgomery County (MD) Department of Fire and Rescue Service for their support of this study.  Alan Butsch,   Brian Rojas,  Michael Johns, Chris Riley

>>>>

Thank you to Chief Scott Goldstein and former Chief Steven Lohr of the Montgomery County (MD) Department of Fire and Rescue Service for their support of this study.  Special appreciation goes to the MCFRS staff that participated in the experiments:    Alan Butsch, Daniel Hudson,  Michael Johns, Steven Neubauer, Sean Regan, Chris Reilly, Bryan Rojtas, Ralph “Dewey” Thomas,  and Douglas Wallace.

The NIST team would like to thank Casey Grant from the Fire Protection Research Foundation and the members of the project technical panel especially John Culbertson, Director, Montana State University Fire Services Training School and Homer Robertson, Deputy Chief, Fort Worth Fire Department.
